---
title: "Circumcision Paper Text"
author: "Paddy O'Toole"
date: "2023-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE}
# libraries
library(dplyr, warn.conflicts = FALSE)

# Metadata 
spec_agegroup <- "15-29"
spec_years <- c(2006, 2020)

ssa_iso3 <- sort(c(
  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
))
```

```{r, echo = FALSE}
# Functions

# change numbers to be expressed in "millions"
to_mill <- \(x) round(x / 1e6, 3)

# change decimal to percentage
to_percentage <- \(x) paste0(round(x * 100, 2), "%")

# translate iso3 to country name
to_cntry_name <- function(x) {
  x_cntry = countrycode::countrycode(x, "iso3c", "country.name")
  # special cases
  case_when(
      x_cntry == "Congo - Brazzaville" ~ "Congo",
      x_cntry == "Congo - Kinshasa"    ~ "DR Congo",
      TRUE                             ~ x_cntry
  )
}

# simplify type
simplify_type <- function(dat) {
  dat %>% 
    mutate(type = case_when(
      grepl("MMC", type) ~ "MMC", 
      grepl("TMC", type) ~ "TMC", 
      TRUE               ~ "MC"
    ))
}
```

# Results

## Subnational Variation in Total, Medical \& Traditional Circumcision over time

```{r, echo = FALSE}
x1 <- readRDS("data/inlines/01_inlines.RDS")
for (i in seq_along(x1)) {
  assign(names(x1)[i], x1[[i]])
}
iso3_lowest_highest_cov <- simplify_type(iso3_lowest_highest_cov)
iso3_cov_diffs <- simplify_type(iso3_cov_diffs)
```

<!-- I surely need to add something about 10-29/15-29 year olds here? -->
<!-- Plot is of 15-29 year olds, but then I talk only about whole pop here -->
In 2006, the year before VMMC programme implementation began, an estimated 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_mill()` 
million men (95\% CI: 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_mill()` 
-
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in the 33 countries in SSA for which we have valid 
circumcision data. 
Of these, 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were MMCS, and 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) were TMCS. 
This contrasts with 2020, where an estimated 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_mill()` 
million males 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in these same countries, of which 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were performed as MMCS, and 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) as TMCS. 
This constituted an increase of 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) newly circumcised males between 2006 and 2020, with 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) new MMCs performed, and 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(upper) %>% to_mill()` 
million) new TMCs performed. 
The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
This translated to a change in mean MC coverage for the SSA region from 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`)
in 2020, or an increase of
`r covs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`).
MMC coverage increased from 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`) 
in 2020, an increase of 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`).
while TMC changed from 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2020, a decrease of
`r covs[[2]] %>% filter(type == "TMC") %>% mutate(mean = mean * -1) %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "TMC") %>% mutate(upper = upper * -1) %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "TMC") %>%  mutate(lower = lower * -1) %>%  pull(lower) %>% to_percentage()`).

<!-- TODO: Need to change this to be filtered by year as well!! -->
MC coverage in each country in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
In contrast, in 2020 MC coverage was estimated to have ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
<!-- Anything else to be said about this? -->

The largest percentage increase in MC coverage from 2006 to 2020 was 
in 
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020,
while the highest percentage increase in MMC was also in 
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020. 
For TMC, the largest percentage decrease between 2006 and 2020 was in 
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020.

The number of annual MCs performed increased from 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2006 to 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2020, a growth of 
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million (
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(lower) %>% to_mill()`
-
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) annually, averaged across all interceding years. 
Amongst these, 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) were MMCs in 2006, while in 2020 
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_mill()` 
million) MMCs were performed, representing an increase in 
million 
(`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) in MMCs performed annually. 
The number of TMCs performed annually did increase slightly from 2006, from 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_mill()` 
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) to 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_mill()`
million
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_mill()`
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_mill()`
million) in 2020. However, 
TMC prevalence actually decreased in many countries from 2006 to 2020. 
<!-- Should I give a number here? -->
This is the focus of section \ref{sec:org5fb5e18}.

*Second Plot* \\
<!-- Want to show here how ??? -->
Within countries, the median difference in MC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
\%,
with the smallest variation in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% last() %>% to_cntry_name()`
(
<!-- `r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% pull(mean) %>% `[[`(2) %>% to_percentage()` -->
