---
title: "Circumcision Paper Text"
author: "Paddy O'Toole"
date: "2023-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- TODO: Change year from 2020 to 2023 -->

```{r, echo = FALSE}
# libraries
library(dplyr, warn.conflicts = FALSE)

# Metadata 
spec_agegroup <- "15-29"
spec_years <- c(2006, 2020)

ssa_iso3 <- sort(c(
  "AGO", "BDI", "BEN", "BFA", "BWA", "CAF", "CIV", "CMR", "COD",
  "COG", "ETH", "GAB", "GHA", "GIN", "GMB", "GNB", "GNQ", "KEN",
  "LBR", "LSO", "MLI", "MOZ", "MWI", "NAM", "NER", "NGA", "RWA",
  "SEN", "SLE", "SWZ", "TCD", "TGO", "TZA", "UGA", "ZAF", "ZMB", "ZWE"
))
```

```{r, echo = FALSE}
# Functions

# change numbers to be expressed in "millions"
to_mill <- \(x) round(x / 1e6, 3)

# change decimal to percentage
to_percentage <- \(x) paste0(round(x * 100, 2), "%")

# translate iso3 to country name
to_cntry_name <- function(x) {
  x_cntry = countrycode::countrycode(x, "iso3c", "country.name")
  # special cases
  case_when(
      x_cntry == "Congo - Brazzaville" ~ "Congo",
      x_cntry == "Congo - Kinshasa"    ~ "DR Congo",
      TRUE                             ~ x_cntry
  )
}

# simplify type
simplify_type <- function(dat) {
  dat %>% 
    mutate(type = case_when(
      grepl("MMC", type) ~ "MMC", 
      grepl("TMC", type) ~ "TMC", 
      TRUE               ~ "MC"
    ))
}
```

# Results

## Subnational Variation in Total, Medical \& Traditional Circumcision over time

```{r, echo = FALSE}
x1 <- readRDS("data/inlines/01_inlines.RDS")
for (i in seq_along(x1)) {
  assign(names(x1)[i], x1[[i]])
}
iso3_lowest_highest_cov <- simplify_type(iso3_lowest_highest_cov)
iso3_cov_diffs <- simplify_type(iso3_cov_diffs)
```

<!-- I surely need to add something about 10-29/15-29 year olds here? -->
<!-- Plot is of 15-29 year olds, but then I talk only about whole pop here -->
In 2006, the year before VMMC programme implementation began, an estimated 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_mill()` 
million men (95\% CI: 
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_mill()` 
-
`r n_circs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in the 33 countries in SSA for which we have valid 
circumcision data. 
Of these, 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were MMCS, and 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) were TMCS. 
This contrasts with 2020, where an estimated 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_mill()` 
million males 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_mill()` 
million) were circumcised in these same countries, of which 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()` 
million) were performed as MMCS, and 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()` 
million) as TMCS. 
This constituted an increase of 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) newly circumcised males between 2006 and 2020, with 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) new MMCs performed, and 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(mean) %>% to_mill()` 
million 
(`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(lower) %>% to_mill()` 
- 
`r n_circs[[2]] %>% filter(type == "TMC") %>% pull(upper) %>% to_mill()` 
million) new TMCs performed. 
The disparity between the number of MCs performed and the number of MMCs performed can be explained by recalling that for five countries, Liberia, Senegal, Niger, Guinea and the Democratic Republic of the Congo, we have no circumcision type information, and so can only estimate MC, not MMC or TMC.
This translated to a change in mean MC coverage for the SSA region from 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`)
in 2020, or an increase of
`r covs[[2]] %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`).
MMC coverage increased from 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()` ) 
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`) 
in 2020, an increase of 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`).
while TMC changed from 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2006, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(mean) %>% to_percentage()` 
(`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(lower) %>% to_percentage()` 
- 
`r covs[[1]] %>% filter(year == 2020, type == "TMC") %>% pull(upper) %>% to_percentage()`)
in 2020, a decrease of
`r covs[[2]] %>% filter(type == "TMC") %>% mutate(mean = mean * -1) %>% pull(mean) %>% to_percentage()` 
(`r covs[[2]] %>% filter(type == "TMC") %>% mutate(upper = upper * -1) %>% pull(upper) %>% to_percentage()` 
- 
`r covs[[2]] %>% filter(type == "TMC") %>%  mutate(lower = lower * -1) %>%  pull(lower) %>% to_percentage()`).

<!-- TODO: Need to change this to be filtered by year as well!! -->
MC coverage in each country in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC in 2006 ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2006) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
In contrast, in 2020 MC coverage was estimated to have ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
while MMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "MMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
and TMC ranged from 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(2) %>% pull(iso3) %>% to_cntry_name()`
to 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(lower) %>% to_percentage()`
- 
(`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(upper) %>% to_percentage()`)
in 
`r iso3_lowest_highest_cov %>% filter(type == "TMC", year == 2020) %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`.
<!-- Anything else to be said about this? -->

The largest percentage increase in MC coverage from 2006 to 2020 was 
in 
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020,
while the highest percentage increase in MMC was also in 
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "MMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "MMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020. 
For TMC, the largest percentage decrease between 2006 and 2020 was in 
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`
at
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(upper) %>% to_percentage()`
-
`r iso3_cov_diffs %>% filter(type == "TMC") %>% slice(1) %>% pull(lower) %>% to_percentage()`),
from 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_percentage()`)
in 2006 to 
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_percentage()`
(`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_percentage()`
-
`r iso3_cov_2006_2020 %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_percentage()`)
in 2020.

The number of annual MCs performed increased from 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2006 to 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) in 2020, a growth of 
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(mean) %>% to_mill()` 
million (
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(lower) %>% to_mill()`
-
`r non_cum_n_performed_diff %>% filter(type == "MC") %>% pull(upper) %>% to_mill()` 
million) annually, averaged across all interceding years. 
Amongst these, 
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) were MMCs in 2006, while in 2020 
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(mean) %>% to_mill()` 
million
(`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed %>% filter(type == "MC", year == 2020) %>% pull(upper) %>% to_mill()` 
million) MMCs were performed, representing an increase in 
million 
(`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_mill()` 
-
`r non_cum_n_performed_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_mill()` 
million) in MMCs performed annually. 
The number of TMCs performed annually did increase slightly from 2006, from 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(mean) %>% to_mill()` 
million 
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(lower) %>% to_mill()` 
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2006) %>% pull(upper) %>% to_mill()` 
million) to 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(mean) %>% to_mill()`
million
(
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(lower) %>% to_mill()`
- 
`r non_cum_n_performed %>% filter(type == "TMC", year == 2020) %>% pull(upper) %>% to_mill()`
million) in 2020. However, 
TMC coverage actually decreased in many countries from 2006 to 2020. 
<!-- Should I give a number here? -->
This is the focus of section \ref{sec:org5fb5e18}.

<!-- *Second Plot* -->
<!-- Want to show here how ??? -->
Within countries, the median difference in MC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(1) %>% pull(area_name)`
,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MC") %>% slice(3) %>% pull(area_name)`.
The median difference within countries in MMC coverage between districts with lowest and highest coverage in 2020 was `r district_diffs_vmmc$median_cov_diffs %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(1) %>% pull(area_name)`,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "MMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "MMC") %>% slice(3) %>% pull(area_name)`.
For TMC coverage, the median difference between districts in 2020 was 
`r district_diffs_vmmc$median_cov_diffs %>% filter(type == "TMC") %>% pull(mean) %>% to_percentage()`
The smallest variation was in
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% last() %>% to_cntry_name()`, 
at
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(mean) %>% to_percentage()`
\%
in
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(2) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(1) %>% pull(area_name)`,
while the largest variation was in 
`r district_diffs_vmmc$country_cov_diffs %>% filter(type == "TMC") %>% pull(iso3) %>% first() %>% to_cntry_name()`, 
at 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(4) %>% pull(area_name)`
to
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(mean) %>% to_percentage()`
\%
in 
`r district_diffs_vmmc$country_cov_highest_lowest %>% filter(type == "TMC") %>% slice(3) %>% pull(area_name)`.
<!-- Anything else? --->

## Subnational Variation in Total, Medical \& Traditional Circumcision across different ages

<!-- TODO: Replace WCA/ECA with VMMC/Non-VMMC -->

Age at circumcision differed greatly by circumcision type and location. 
The age group which experienced the greatest increase in MC coverage from 2006, the year before VMMC programme implementation began (reference), to 2020 was 
x, 
reflecting VMMC focus on these ages. 
The age group with the highest MC coverage in 2020 was 
x, 
in contrast to 2006, where this age group was 
x. 
The age group with the highest MMC coverage in 2020 was 
x, 
while for TMC coverage this age group was 
x. 
The average age of MC in 2020 in SSA was 
x, 
compared to 
x 
in 2006. 
For MMC, the average age at circumcision in 2020 was 
x, 
compared to 
x 
in 2006, while for TMC the average age was 
x 
in 2020, compared to 
x 
in 2006. 
The average age of MC in 2020 for ESA was 
x, 
while in WCA it was 
x. 

## Subnational Heterogeneity in Age at Medical and Traditional Circumcision

Fill in!

## Decrease in TMC in SSA region Over Time

The average TMC coverage in SSA in 2006 was 
x
\% (
x
\% to 
x
\%). 
This fell to 
x
\% (
x
\% to 
x
\%) in 2020, representing a decrease of 
x
\% (
x
\% to 
x
\%). 
In ESA, TMC coverage was 
x
\% (
x
\% to 
x
\%) in 2006, compared to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) decrease. 
In constrast, TMC coverage in WCA was 
x
\% (
x
\% to 
x
\%) versus 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) fall. 
In 2006, 
x 
(
x 
to 
x
) TMCs were performed, while in 2020 this was reduced to 
x 
(
x to 
x
), representing a 
x (
x
to
x
) decrease in annual TMCs.
In ESA, the annual number of TMCs performed dropped from 
x
(
x
to 
x
) in 2006 to 
x
(
x
to 
x
) in 2020, a 
x 
(
x
to 
x
) drop. 
In WSA, this number fell from 
x 
(
x 
to 
x
) in 2006 to 
x 
(
x
to 
x
) in 2020, a fall of 
x
(
x
to 
x
).
<!-- TODO: Change to 15-29, right? -->
For the 10-29 age group, TMC coverage was reduced from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a drop of 
x
\% 
(
x
\% to 
x
\%).
In VMMC countries, this was reduced from 
x
\% (
x
\% to 
x
\%) to 
x
\% (
x
\% to 
x
\%) from 2006 to 2020, while even in non-VMMC countries this decreased from 
x
\% (
x
\% to 
x
\%) to 
x
\% (
x
\% to 
x
\%). 
The largest decrease in TMC coverage from 2006 to 2020 was in 
x
, from 
x
\% (
x
\% to 
x
\%) to 
x
\% (
 x 
\% to 
 x 
\%). 
[If the above is a VMMC country] The largest decrease in TMC coverage amongst non-VMMC countries was from 
x 
\% (
x 
\% to 
x 
\%) to 
x 
\% (
x 
\% to 
x 
\%) in 
x 
. 

## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries

Amongst the 13 VMMC priority countries modelled, just 
x
 countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
x
 and 
x
. 
MC coverage across these countries increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020. 

x
 (
x
 to 
x
) circumcisions were performed between 2007 and 2020 in these countries. 
Of these, 
x
 (
x
 to 
x
) were MMCs. 
No countries were e
x
pected to have reached this goal in all districts. 
The number of annual MCs increased from 
x
 (
x
 to 
x
) in 2006 to 
x
 (
x
 to 
x
) in 2020. 

x
 (
x
 to 
x
) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, 
x
 (
x
 to 
x
) times the projected number of MCs for 2020. 
The largest increase in MC coverage amongst VMMC priority countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 

However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC prioirty countries. 

x
/
x
 districts in these countries were e
x
pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
x
/
x
 in 2006, before VMMC programmes began. 
Even in 
x
, where MC was projected to be lowest in 2020, 
x
/
x
 districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
MC coverage there increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 
